Efficient static analysis of Marlowe contracts

### 2020-05-04 papers/static_analysis2020/paper.tex
Fix typo
Fix broken sentence

We cannot just constrain the maximum slot number of the first transaction
to be less than the timeout in the \texttt{When} because, if we do
that, then we will miss executions where one transaction expires several
\texttt{When} in a row, or when it expires one \texttt{When} and provides
the right input for later \texttt{When}. And we cannot not constrain
the maximum slot number of the first transaction because then we will
not know whether the first transaction goes beyond the \texttt{When}
or not.

@@

One subtle detail that we realised during testing is that, even though
the diagram above shows that a \texttt{When} belongs to the next transaction,
because it will still be there after the previous transaction is executed,
the observations in the \texttt{Notify} cases. In the same way, the
values in the \texttt{Deposit} cases will refer to the \texttt{State}
before the \texttt{When} is executed, but to the slot interval of
the transaction that triggers the \texttt{When}, since the amount
to deposit must be calculated without considering the effects of the
deposit itself.

>>>>

We cannot just constrain the maximum slot number of the first transaction
to be less than the timeout in the \texttt{When} because, if we do
that, then we will miss executions where one transaction expires several
\texttt{When} in a row, or where it expires one \texttt{When} and provides
the right input for later \texttt{When}. And we cannot not constrain
the maximum slot number of the first transaction because then we will
not know whether the first transaction goes beyond the \texttt{When}
or not.

@@

One subtle detail that we realised during testing is that, even though
the diagram above shows that a \texttt{When} belongs to the next transaction,
because it will still be there after the previous transaction is executed,
the observations in the \texttt{Notify} cases will correspond to the
\texttt{State} before the \texttt{When} is executed, but to the slot
interfal of the transactions that triggers the \texttt{When}. The same
is true for \texttt{Value}s in the \texttt{Deposit} cases, since the amount
to deposit must be calculated without considering the effects of the
deposit itself.
